---
title: "plotly"
author: "Qixiang Chen"
date: "11/6/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(dplyr)
library(rnoaa)
```


```{r}
weather_df =
rnoaa::meteo_pull_monitors(
 c("USW00094728", "USC00519397", "USS0023B17S"),
 var = c("PRCP", "SNOW", "SNWD", "TMAX", "TMIN"),
 date_min = "2020-01-01",
date_max = "2020-12-31") %>%
 mutate(
name = recode(
 id,USW00094728 = "CentralPark_NY", USC00519397 = "Waikiki_HA", USS0023B17S = "Waterhole_WA"),tmin = tmin / 10,tmax = tmax / 10) %>%
  distinct() %>%
  replace_na(list(prcp = 0, snow = 0, snwd = 0)) %>%
  drop_na(tmax, tmin) %>%
  select(name, id, everything())
weather_df
```
```{r}
weather_month = 
  weather_df %>%
  mutate(date2 = date) %>%
  separate(date2, into = c("year", "month", "day"), sep = "-") %>%
  mutate(year = as.numeric(year),
         month = as.numeric(month),
         day = as.numeric(day)) %>%
  mutate(month = case_when(month == 1 ~ "Jan",
                           month == 2 ~ "Feb",
                           month == 3 ~ "Mar",
                           month == 4 ~ "Apr",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "Aug",
                           month == 9 ~ "Sept",
                           month == 10 ~ "Oct",
                           month == 11 ~ "Nov",
                           month == 12 ~ "Dec",
                           )) %>%
  mutate(month= forcats::fct_relevel(month, "Jan", "Feb", "Mar", "Apr", "May", "June", "July", "Aug", "Sept", "Oct",
                                          "Nov", "Dec"))
weather_month %>%
  filter(id == "USW00094728") %>%
  mutate(text_label = str_c("precipitation: ", prcp, "\ndate: ", date, "\nsnow: ", snow)) %>%
  plot_ly(x = ~tmin, y = ~tmax, color = ~month, text = ~text_label, alpha = 0.3, type = "scatter", mode = "markers", 
          colors = "viridis")
```

This scatter plot can provide us the information about the distribution of the max temperature and the min temperature of Central Park in New York City for the whole 2020. In this case, x-axis represents the minimum temperature of the day, and y-axis represents the maximum temperature of the day. If a point is close to the line y = x, that means its max temperature and its min temperature are close to each other, which implies a relative small fluctuation in temperature change. 

```{r}
weather_month %>%
  filter(id == "USW00094728") %>%
  mutate(text_label2 = str_c("date: ", date, "\nlocation: ", name)) %>%
  plot_ly(y = ~prcp, x = ~month, text = ~text_label2, color = ~month, type = "box")
```

The plot shows the distribution of monthly precipitation in the Central Park of NYC in the year 2020.

```{r}
wider_prcp_df = 
  weather_month %>%
  select(name, id, date, prcp, month) %>%
  pivot_wider(
    names_from = month,
    values_from =prcp
  ) %>%
  select(-date)
prcp_sum_df = 
  wider_prcp_df %>%
  mutate(
    Jan = sum(wider_prcp_df$Jan, na.rm = TRUE),
    Feb = sum(wider_prcp_df$Feb, na.rm = TRUE),
    Mar = sum(wider_prcp_df$Mar, na.rm = TRUE),
    Apr = sum(wider_prcp_df$Apr, na.rm = TRUE),
    May = sum(wider_prcp_df$May, na.rm = TRUE),
    June = sum(wider_prcp_df$June, na.rm = TRUE),
    July = sum(wider_prcp_df$July, na.rm = TRUE),
    Aug = sum(wider_prcp_df$Aug, na.rm = TRUE),
    Sept = sum(wider_prcp_df$Sept, na.rm = TRUE),
    Oct = sum(wider_prcp_df$Oct, na.rm = TRUE),
    Nov = sum(wider_prcp_df$Nov, na.rm = TRUE),
    Dec = sum(wider_prcp_df$Dec, na.rm = TRUE),
  )
prcp_sum_df = prcp_sum_df[1,]
prcp_sum_df = 
  prcp_sum_df %>%
  pivot_longer(
    Jan:Dec,
    names_to = "month",
    values_to = "prcp"
  )
prcp_sum_df %>%
  mutate(month= forcats::fct_relevel(month, "Jan", "Feb", "Mar", "Apr", "May", "June", "July", "Aug", "Sept", "Oct",
                                          "Nov", "Dec")) %>%
  plot_ly(x = ~month, y = ~prcp, color = ~month)
```

The plot shows the distribution of total monthly rainfall in the Central Park of NYC in year 2020.
